Inverse energy transfer in three-dimensional quantum vortex flows

### 2025-06-26 main_REV.tex
Updated figure

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{blindtext}
\usepackage{float}
\usepackage{caption,cancel}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{xcolor}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal poi<?xml version="1.0" encoding="UTF-8" standalone="no"?>
<!-- Created with Inkscape (http://www.inkscape.org/) -->

<svg
   version="1.1"
   id="svg2379"
   width="18.273407"
   height="12.954988"
   xmlns:inkscape="http://www.inkscape.org/namespaces/inkscape"
   xmlns:sodipodi="http://sodipodi.sourceforge.net/DTD/sodipodi-0.dtd"
   xmlns="http://www.w3.org/2000/svg"
   xmlns:svg="http://www.w3.org/2000/svg">
  <defs
     id="defs2383" />
  <sodipodi:namedview
     id="namedview2381"
     pagecolor="#ffffff"
     bordercolor="#666666"
     borderopacity="1.0"
     inkscape:pageshadow="2"
     inkscape:pageopacity="0.0"
     inkscape:pagecheckerboard="0" />
  <inkscape:clipboard
     style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:14.42808189px;line-height:1.25;font-family:'Liberation Sans';font-variant-ligatures:normal;font-variant-position:normal;font-variant-caps:normal;font-variant-numeric:normal;font-variant-alternates:normal;font-variant-east-asian:normal;font-feature-settings:normal;font-variation-settings:normal;text-indent:0;text-align:start;text-decoration-line:none;text-decoration-style:solid;text-decoration-color:#000000;letter-spacing:normal;word-spacing:normal;text-transform:none;writing-mode:lr-tb;direction:ltr;text-orientation:mixed;dominant-baseline:auto;baseline-shift:baseline;white-space:normal;opacity:1;vector-effect:none;fill:#000000;fill-opacity:1;stroke:#000000;stroke-width:0.7802948;stroke-linecap:butt;stroke-linejoin:miter;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1;-inkscape-stroke:none;stop-color:#000000;stop-opacity:1;-inkscape-font-specification:'Liberation Sans'"
     min="18.259847,226.98512"
     max="36.533254,239.94011"
     geom-min="18.649995,227.37527"
     geom-max="36.143107,239.54997" />
  <g
     id="g2385"
     transform="matrix(3.7795276,0,0,3.7795276,-18.259848,-226.98513)">
    <text
       xml:space="preserve"
       style="font-style:normal;font-weight:normal;font-size:3.81743px;line-height:1.25;font-family:sans-serif;fill:#000000;fill-opacity:1;stroke:#000000;stroke-width:0.206453;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
       x="4.2326026"
       y="69.187035"
       id="text37212-4"
       transform="scale(1.104076,0.90573475)"><tspan
         sodipodi:role="line"
         id="tspan37210-3"
         style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-family:'Liberation Sans';-inkscape-font-specification:'Liberation Sans';stroke:#000000;stroke-width:0.206453;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
         x="4.2326026"
         y="69.187035">(b)</tspan></text>
  </g>
</svg>
t
\usepackage{bm}% bold math
\usepackage{blindtext}
\usepackage{float}
\usepackage{caption,cancel}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{xcolor}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
